---
title: "PCA"
output: html_document
---

This document includes the process for performing PCA on clusters. It requires some tweaking as all clusters seem to group at present. Among the things I need to figure out is how to eliminate stop words from the bag of words.

```{r}

#Streamlined PCA Code
stopWords = stopwords("en")
wordCutoff = 10
df = poemswithBY %>% mutate(V1 = as.character(V1))
clusterWords = getWords(df) 
counts = clusterWords %>% mutate(word=tolower(word)) %>% group_by(V1,word) %>% dplyr::summarize(count=n()) %>% ungroup
td = allWordsIntoTD(clusterWords,normalized = T) 
justaMatrix = td %>% select(-V1)
model = prcomp(justaMatrix)
prediction = predict(model)
prediction = prediction %>% 
  as.data.frame %>% mutate(cluster=td$V1 %>% as.character) %>% 
  select(cluster,PC1,PC2,PC3)






```

See the Principal Components

```{r}

#We can see what the weights are by 
model$rotation %>% as.data.frame %>% mutate(word=rownames(model$rotation)) %>% select(word,PC1) %>% arrange(-PC1) %>% head
model$rotation %>% as.data.frame %>% mutate(word=rownames(model$rotation)) %>% select(word,PC1) %>% arrange(PC1) %>% head
# The second "Principal Component"
model$rotation %>% as.data.frame %>% mutate(word=rownames(model$rotation)) %>% select(word,PC2) %>% arrange(-PC2) %>% head
model$rotation %>% as.data.frame %>% mutate(word=rownames(model$rotation)) %>% select(word,PC2) %>% arrange(PC2) %>% head

```


Visualize using a variety of methods

```{r}

#Visualize (Need to get V1 Cluster number into the mix)

ggplot(prediction) + geom_point(aes(x=PC1,y=PC2,color=cluster))
ggplot(prediction %>% mutate(V1=cluster) %>% inner_join(df) %>% filter(n()>5)) + geom_text(aes(x=PC1,y=PC2,label=V1))
ggplot(prediction %>% mutate(url=url) %>% inner_join(df)) + geom_point(aes(x=PC2,y=PC3,shape=username,color=username,size=5))
ggplot(prediction %>% mutate(url=url) %>% inner_join(df) %>% group_by(username) %>% filter(n()>5)) + geom_text(aes(y=PC1,x=as.Date(Date),color=username,size=5,label=username))

ggplot(prediction %>% mutate(url=url) %>% inner_join(df) %>% group_by(username) %>% filter(n()>5)) + geom_text(aes(y=PC1,x=PC2,color=username,size=5,label=username))

#Print df header
head(prediction)

#Select a row to print
df[10,]



```

This requires more work, but here is the alternative to ggplot that Abby suggested. It seems promising, but I'm not yet able to get it to work.

```{r}

#Visualize with ggbiplot (???)
data(halfCluster)
clusters.pca <- prcomp(halfCluster, scale. = TRUE)
ggbiplot(clusters.pca, obs.scale = 1, var.scale = 1,
         groups = halfCluster.V1, ellipse = TRUE, circle = TRUE) +
  scale_color_discrete(name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')


```

